\documentclass[a4paper]{article}

\usepackage{tabularx}

%\usepackage{doublespace}
%\setstretch{1.2}
\usepackage{makeidx}
\usepackage{ae}
\usepackage{url}
\usepackage[T1]{fontenc}
\usepackage{CV}

\begin{document}

\pagestyle{empty}

%Ueberschrift
\begin{center}
\huge{\textsc{Curriculum Vitae}}
\vspace{\baselineskip}

\Large{\textsc{Amir Hossein Ghamarian}}
\end{center}
\vspace{1.5\baselineskip}

\section{Address}

\begin{flushleft}
  University of Twente \\
  Department of Computer Science, \\
  P.O. Box 217, NL-7500 AE (Zilverling 5070), \\
  Enschede, The Netherlands \\
  Phone: +31-53-489 4702 \\
  Fax: +31-53-489 3247 \\
  Email: a.h.ghamarian@cs.utwente.nl \\
\end{flushleft}

\section{Personal Information}
\begin{flushleft}
  Gender: Male \\
  Date of birth: 19th of September, 1978 \\
%  Place of birth: Tehran, Iran \\
%  Nationality:: Iranian \\
%  Marital Status: Single
\end{flushleft}


\section{Education}
\begin{CV}
\item[2/2003--8/2008] Ph.D., Electrical Engineering, Eindhoven
University of Technology, Eindhoven, The Netherlands.

\item[9/2000--1/2003] M.Sc., Computer Science, Sharif University of Technology, Tehran, Iran.

\item[9/1996--9/2000] B.Sc., Computer Engineering, Sharif University
of Technology, Tehran, Iran.

%\item[9/1992--05/1996] Diploma, Mathematics and Physics, Peyvand
%High School, Tehran, Iran.
\end{CV}
\pagebreak

\section{Professional Experience}

\begin{CV}
\item[4/2009--Now]Postdoc, Computer Science, Twente University of
Technology, Enschede, The Netherlands \\
Projects: Various projects on both theoretical and practical aspects of graph transformation
\begin{itemize}
  \item Incremental pattern matching: developing algorithms and implementation
  \item Compositional graph transformation: Enhancing the existing research and the implementation is on going.
  \item Planning: Incorporation of planning algorithms in graph transformation
\end{itemize}
\item[2/2008--4/2009] Postdoc, Electrical Engineering, Eindhoven University
of Technology, Eindhoven, The Netherlands. \\
Project: A parameterized compositional multi-dimensional multiple-choice knapsack heuristic for CMP run-time management

\item[2/2003--2/2008] Ph.D., Electrical Engineering, Eindhoven
University of Technology, Eindhoven, The Netherlands.\\
Project: Developing both theoretical and practical aspects of timing analysis of data flow graphs
and enabling them to be used for execution time estimation of multimedia applications running on multiprocessors.

\item[08/2001--01/2003] Software Designer/Developer, Sharif Computing Center, Sharif University of Technology, Tehran,
Iran.\\
Project: An internet based software for course registration of
universities.
\end{CV}



\section{Teaching Experience}
\begin{CV}
\item [University of Twente]:

\hspace{-2cm}\parbox{\textwidth}{
\begin{itemize}
    \item 192135201: Formal methods for software engineering, TA, (2x)
    \item 192111801: Basic modeling in informatics, TA, (1x)
    \item 192140200: Algorithm, data structures and complexity, TA, (2x)
\end{itemize}}
\item [Eindhoven University of Technology]:

\hspace{-2cm}\parbox{\textwidth}{
\begin{itemize}
    \item 5MC10: Combinatorial Algorithms, TA, (4x)
    \item 5AE12: TIO First year (Optimization), TA, (2x)
\end{itemize}}
\item [Sharif University of Technology]:

\hspace{-2cm}\parbox{\textwidth}{
\begin{itemize}
    \item 22815: Advanced Programming, Lecturer, (2x)
    \item 40224: Data Structures, Lecturer, (1x)
\end{itemize}}
\end{CV}



\section{Publications}
\begin{itemize}
\item Amir Hossein Ghamarian, Maarten de Mol, Arend Rensink, Eduardo
Zambon and Maria Zimkova. ``Modeling and Analysis Using GROOVE." \emph{
International Journal on Software Tools for Technology Transfer},
online pre-publication 2011. ISSN 1433-2779

\item Amir Hossein Ghamarian, Arash Jalali, and Arend Rensink. ``Incremental
Pattern Matching in Graph-based State Space Exploration." \emph{In: Proceedings of the Fourth
International Workshop on Graph-Based Tools (GraBaTs 2010)}, 28 Sept 2010, Enschede, The Netherlands.

\item Hamid Shojaei, Amir Hossein Ghamarian, Twan Basten, Marc Geilen, Sander Stuijk and Rob Hoes.
``A parameterized compositional multi-dimensional multiple-choice knapsack heuristic for CMP run-time management",
\emph{Design Automation Conference, DAC 09}, San Francisco, CA, USA, July 26-31, 2009.

\item Sander Stuijk, Twan
Basten, Marc Geilen, Amir Hossein Ghamarian, Bart Theelen.
``Resource-Efficient Routing and Scheduling of Time-Constrained
Streaming Communication on Networks-on-Chip." \emph{Journal of
Systems Architecture.} 54(3-4):411-426, March-April 2008. (Special
section on Programming Models and Architectures for Embedded
Systems.)

\item Amir Hossein Ghamarian, Marc Geilen, Twan
Basten, Sander Stuijk. ``Parametric Throughput Analysis of
Synchronous Data Flow Graphs." \emph{Design, Automation and Test in
Europe, DATE 08}, Munich, Germany. March 10-14, 2008.

\item Amir Hossein Ghamarian, Marc Geilen, Sander Stuijk, Twan
Basten, Bart Theelen. ``Latency Minimization of Synchronous Data
Flow Graphs." \emph{10th Euromicro Conference on
Digital System Design, DSD 07}, Lubeck, Germany. August 27-31, 2007.

\item Amir Hossein Ghamarian, Marc Geilen, Sander Stuijk, Twan
Basten, Bart Theelen. ``Liveness and Boundedness of Synchronous Data
Flow Graphs." \emph{Formal Methods in Computer Aided Design, FMCAD
06}, San Jose, California, USA, November 12-16, 2006.

\item Sander Stuijk, Twan Basten, Marc Geilen, Amir Hossein Ghamarian and Bart D.
Theelen. ``Resource-Efficient Routing and Scheduling of
Time-Constrained Network-on-Chip Communication." \emph{9th Euromicro
Conference on Digital System Design, DSD 06}, Dubrovnik, Croatia,
30th August- 1st September, 2006.

\item Amir Hossein Ghamarian, Marc Geilen, Sander Stuijk, Twan Basten, Arno Moonen, Marco Bekooij, Bart Theelen, MohammadReza Mousavi.
``Throughput Analysis of Synchronous Data Flow Graphs." \emph{Sixth
International Conference on Application of Concurrency to System
Design, ACSD 06}, Turku, Finland, June 11-13, 2006.

\item Amir Hossein Ghamarian, ``An Evolutionary Algorithm for Graph
Coloring", \emph{M.S. Thesis}, Mathematical Sciences Department,
Sharif University of Technology, Tehran, Iran, January 2003 (in
Persian).

\item Amir Hossein Ghamarian, ``A Linux-based SMTP/POP3 Proxy", \emph{B.S.
Thesis}, Computer Engineering Department, Sharif University of
Technology, Tehran, Iran, September 2001 (in Persian).
\end{itemize}


\section{Awards and Scholarship}

\begin{itemize}

\item Admission with scholarship for a Ph.D. program,
Eindhoven University of Technology, Eindhoven, The Netherlands,
Febuary 2003.

\item Rank 17 in the National Computer Science Graduate Studies
Entrance Exam in Iran, April 2000.
\end{itemize}

\section{Interested Research Areas}
\begin{itemize}

\item Formal methods (Graph transformation and Model checking)

\item Models of Computation/Concurrency for Embedded Systems

\item Real-Time issues, Performance modelling, Design Space
Exploration

%\item Multiprocessor on-a-chip, On-Chip networks, Heterogeneous
%and Reconfigurable systems
\end{itemize}


\section{Skills}
\begin{itemize}
\item Structured Analysis and Design.

\item Object Oriented Modelling (in UML).

\item C, C++, Java, Haskell, Prolog.

\item Microsoft Visual C++ MFC, Eclipse IDE

\item Model checking tools (SPIN, UPAAL), Java profiling tools (YourKit)

\item \TeX-based Typesetting Systems.

\item Test Driven Development (TDD), Software Design Patterns, Service Oriented Architecture (SOA)

%\item continuation integration

\item Version control softwares (SVN, CVS)
\end{itemize}

\section{Engineering Associations}
\begin{itemize}

\item Member of The Institute of Electrical and Electronics
Engineers (IEEE).

\item Member of IPA (Dutch Institute for Programming research and Algorithmics)

\end{itemize}

\section{Language Familiarities}
\begin{CV}
\item [English] Fluent
\item [Dutch] Intermediate
\item [French] Minimum knowledge
\item [Farsi (Persian)]  Mother tongue
\end{CV}

\section{Hobbies and Interests}
\begin{itemize}
  \item Soccer and Tennis
  \item Music
  \item Movies
\end{itemize}

\section{\bf References}
\begin{enumerate}
\item Prof.Dr.ir. Arend Rensink\\
Department of Computer Science, \\
University of Twente, P.O. Box 217, \\
NL-7500 AE Enschede,
the Netherlands. \\
Phone: +31 53 489 4862 \hspace*{1cm} Fax: +31 53 489 3247 \\
e-mail:\url{mailto:rensink@cs.utwente.nl}  \\
web: \url{http://wwwhome.cs.utwente.nl/~rensink/}

\item Prof.Dr.ir. Twan Basten\\
Department of Electrical Engineering, \\
TU Eindhoven, P.O. Box 513, \\
5600 MB Eindhoven,
the Netherlands.\\
Phone:+31 40 2475782  \hspace*{1cm}    Fax:+31 40 2433066   \\
  e-mail:\url{mailto:a.a.basten@tue.nl} \\
web: \url{http://www.es.ele.tue.nl/~tbasten/}

\item Dr.ir. Marc Geilen\\
Department of Electrical Engineering, \\
TU Eindhoven, P.O. Box 513, \\
5600 MB Eindhoven,
the Netherlands.\\
Phone:+31 40 2473091  \hspace*{1cm}    Fax:+31 40 2433066   \\
  e-mail:\url{mailto:M.C.W.Geilen@tue.nl
} \\
web: \url{http://www.es.ele.tue.nl/~mgeilen/}

\item Prof.dr. Amir Daneshgar\\
Department of Mathematical Sciences,\\
Sharif University of Technology,\\
P.O. Box 11365-9415,\\
Tehran, Iran.\\
Phone:+98 21 6616-5610 \hspace*{1cm}    Fax:+98 21 66005117 \\
e-mail:\url{mailto:daneshgar@sharif.ac.ir}\\
web: \url{http://mathsci.sharif.edu/daneshgar/}

%\item Prof.dr.ir. Ralph Otten\\
%Department of Electrical Engineering, \\
%TU Eindhoven, P.O. Box 513, \\
%5600 MB Eindhoven,
%the Netherlands.\\
%Phone:+31 40 2473959\hspace*{1cm}    Fax:+31 40 2433066 \\
%e-mail:\url{mailto:r.h.j.m.otten@tue.nl}\\
\end{enumerate}


\end{document}
