% LaTeX resume using res.cls
\documentclass[margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textwidth}{5.1in} % set width of text portion

\begin{document}

% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf Amir H. Ghamarian}
% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:
 \moveleft.5\hoffset\centerline{Gustav Mahlerlaan 429}
 \moveleft.5\hoffset\centerline{Amsterdam, 1082MK}
 \moveleft.5\hoffset\centerline{06 17978678}


\begin{resume}
 
\section{OBJECTIVE}  A position in the field of computers with special 
                interests in business applications programming, 
                information processing, and management systems. 

\section {Personal  \\ Information} Gender: Male \\
                                    Date of Birth: 19th of September, 1978 \\
				    Citizenship: Dutch
 
\section{Language  \\ Familiarities} English: Fluent \\
				     Dutch: Workign knowledge (B2/C1) \\
				     Farsi: Native


\section{EDUCATION} {\sl Ph.D } Electrical Engineering,  \hfill Feb. 2003 - Aug. 2008 \\
                      % \sl will be bold italic in New Century Schoolbook (or
	              % any postscript font) and just slanted in
		      %	Computer Modern (default) font
			Eindhoven University of Technology, Eindhoven, The Netherlands. 


	{\sl M.Sc. } Computer Science,  \hfill Sep. 2000 - Jan. 2003 \\
 		Sharif University of Technology,  Tehran, Iran.
                      % \sl will be bold italic in New Century Schoolbook (or
	              % any postscript font) and just slanted in
		      %	Computer Modern (default) font

	{\sl B.Sc. } Computer Engineering,  \hfill Sep. 1996 - Sep. 2000 \\
 		Sharif University of Technology, Tehran, Iran.
 

 
\section{COMPUTER \\ SKILLS} {\sl Languages \& Software:} COBOL, IFPS, Focus, 
         Megacalc, Pascal, Modula2, C, APL, SNOBOL, 
                FORTRAN, LISP, SPIRES, BASIC, VSPC Autotab, 
                IBM 370 Assembler, Lotus 1-2-3. \\
                {\sl Operating Systems:} MTS, TSO, Unix. 
 
\section{EXPERIENCE} 

 		{\sl Chief Technology Officer} \hfill Des. 2017 - Present \\
		Machine2learn, Amsterdam, The Netherlands \\
		Design of various aspects of adaptive predictive analytics manager of Pega 7 (One of the major component of Pega decision manager). 
		Most notable project was re- designing the system from a single node web-application to a multinode, cloud based, resilient, and scalable design. \\
		\emph{Technologies:} Python, Javascript, C++, Swift, Bash, Linux, Docker, Kubernetes, Various deep learning and machine learning packages (Scikit learn, matplotlib, numpy, Tensorflow, PyTorch, FastAi, ...), Vue, OpenCV, R.
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Developed four ``user friendly" forecasting 
                    systems each of which produces 18 to 139 
                    individual reports. 
                \item   Developed or improved almost all IFPS 
                    programs used for financial reports. 
                \end{itemize}


 		{\sl Senior Software Engineer} \hfill Sept. 2014 - Dec. 2017 \\
		Pegasystems, Amsterdam, The Netherlands \\
		Design of various aspects of adaptive predictive analytics manager of Pega 7 (One of the major component of Pega decision manager). 
		Most notable project was re- designing the system from a single node web-application to a multinode, cloud based, resilient, and scalable design. \\
		\emph{Technologies:} Java, Cassandra, BDD, TDD, Gradle, Git, Docker, Jenkins, Pega, Hazelcast, Postgresql, Tomcat and RxJava.
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Developed four ``user friendly" forecasting 
                    systems each of which produces 18 to 139 
                    individual reports. 
                \item   Developed or improved almost all IFPS 
                    programs used for financial reports. 
                \end{itemize}
 
                {\sl Senior Design Engineer} \hfill          Feb. 2014 - Apr. 2015 \\
		ASML, Veldhoven, The Netherlands \\
		Worked in the wafer stage team. I was responsible for designing the first model driven driver for a new hardware component \\
		\emph{Technologies:} C, C++, Python, ClearCase, Make, Vim, Bash, Model-based development, Solaris.
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Performed computer aided statistical analysis 
                    of data. 
                 \end{itemize} 

                {\sl Senior Software Engineer} \hfill        Apr. 2012 - Feb. 2013 \\
		Cordys (Now OpenText), Putten, The Netherlands \\
		Worked in Collaborative Workspace team, which was the main framework provided the main infrastructure for other components of the system. \\
		\emph{Technologies:} Java, Javascript, Jenkins, Ant, TDD.
                  \begin{itemize}
                   \item Recognized need for, developed, and wrote 
                    employee training manual. Performed various 
                    duties including cooking, employee training, 
                    ordering, and inventory control. 
                   \end{itemize} 

		{\sl Senior Software Engineer} \hfill        Apr. 2012 - Feb. 2013  \\
		Cordys (Now OpenText), Putten, The Netherlands \\
		Worked in Collaborative Workspace team, which was the main framework provided the main infrastructure for other components of the system.  
                  \begin{itemize}
                   \item Recognized need for, developed, and wrote 
                    employee training manual. Performed various 
                    duties including cooking, employee training, 
                    ordering, and inventory control. 
                   \end{itemize} 
 
\section{COMMUNITY \\ SERVICE}  Organized and directed the 1988 and 1989 Grand 
                 Marshall Week \newline ``Basketball Marathon.'' A 24 hour 
                charity event to benefit the Troy Boys Club. Over 
                250 people participated each year. 

\section{EXTRA-CURRICULAR \\ ACTIVITIES}             
            Elected {\it House Manager}, Rho Phi Sorority \\
            Elected {\it Sports Chairman} \\
            Attended Krannet Leadership Conference \\
                Headed delegation to Rho Phi Congress \\
                Junior varsity basketball team \\
                Participant, seven intramural athletic teams 
 

\end{resume}
\end{document}




