\section{Professional Experience}

%\begin{CV}
Senior Software Engineer \hfill Sep. 2014 - Present \\
Pegasystems, Amsterdam, The Netherlands \\
Design of various aspects of adaptive predictive analytics manager of Pega 7 (One of the major component of Pega decisioning). Most notable project was redesining the system from a single node web-application to a multinode, cloud based, resilient, and scalable design. \\
Technologies/Methodologies: Java, Cassandra, BDD, TDD, Gradle, Git, Jenkins, Pega, and Hazelcast.

Senior Design Engineer  \hfill Feb. 2014 - Apr. 2015 \\
ASML, Veldhoven, The Netherlands \\
Worked in the wafer stage team. I was responsible for designing the first model deriven driver for a new hardware component \\
Technologies/Methodologies: C, C++, Python, ClearCase, Make, Vim, Bash and Solaris.

Senior Software Engineer  \hfill Apr. 2012 - Feb. 2013 \\
Cordys (Now OpenText), Putten, The Netherlands \\
Worked Collaborative Workspace team, which was the main framework provided the main infrastructure for other components of the system. \\
Technologies/Methodologies: Java, Javascript, Jenkins, Ant, TDD.

Postdoc in Formal methods  \hfill Apr. 2009 - Apr. 2012 \\
Twente University of Technology, Enschede, The Netherlands  \\
\ifindustry
Project: Various projects on both theoretical (Graph theory and algorithms, Set theory, Combinatorics, Category theory, model checking) and practical aspects of graph transformation. 
Most projects involved java implementations as well which have been done as part of graph transformation tool GROOVE (\url{http://groove.cs.utwente.nl/}).  \\
Teaching: Various courses on Algorithms, Advanced logic, programming, software engineering and formal methods. \\
Other activities: Mentoring several master and phd students in their research projects as well as organizing scientific workshops.
\fi

Postdoc in Embedded systems  \hfill Feb. 2008 - Apr. 2009 \\
Eindhoven University of Technology, Eindhoven, The Netherlands \\
\ifindustry
Project: Developing a parameterized compositional heuristic algorithm for chip multiprocessor run-time management, involving mathematical modelling and programming in C++.\\
Teaching: Various courses on Algorithms, data structures, linear programming and combinatorics \\
Other activities: Mentoring several master and phd students in their research projects as well as organizing scientific workshops.
\fi

Ph.D., Eindhoven University of Technology. \hfill Feb. 2003 - Feb. 2008 \\
Electrical Engineering Department, Eindhoven, The Netherlands \\
\ifindustry
Project: Developing both theoretical and practical aspects of timing analysis of data flow graphs
and enabling them to be used for execution time estimation of multimedia applications running on multiprocessors.
The project invovlved several subprojects which have been implemented in C++ over Linux.
\fi

Software Designer/Developer  \hfill Aug. 2001 - Jan. 2003 \\
Sharif Computing Center, Sharif University of Technology, Tehran, Iran. \\
\ifindustry
Project: An internet based software for course registration of universities using Java and J2EE.
\fi
