\section{Publications}
\begin{itemize}
\item Amir Hossein Ghamarian, Maarten de Mol, Arend Rensink, Eduardo
Zambon and Maria Zimkova. ``Modeling and Analysis Using GROOVE." \emph{
International Journal on Software Tools for Technology Transfer},
online pre-publication 2011. ISSN 1433-2779

\item Amir Hossein Ghamarian, Arash Jalali, and Arend Rensink. ``Incremental
Pattern Matching in Graph-based State Space Exploration." \emph{In: Proceedings of the Fourth
International Workshop on Graph-Based Tools (GraBaTs 2010)}, 28 Sept 2010, Enschede, The Netherlands.

\item Hamid Shojaei, Amir Hossein Ghamarian, Twan Basten, Marc Geilen, Sander Stuijk and Rob Hoes.
``A parameterized compositional multi-dimensional multiple-choice knapsack heuristic for CMP run-time management",
\emph{Design Automation Conference, DAC 09}, San Francisco, CA, USA, July 26-31, 2009.

\item Sander Stuijk, Twan
Basten, Marc Geilen, Amir Hossein Ghamarian, Bart Theelen.
``Resource-Efficient Routing and Scheduling of Time-Constrained
Streaming Communication on Networks-on-Chip." \emph{Journal of
Systems Architecture.} 54(3-4):411-426, March-April 2008. (Special
section on Programming Models and Architectures for Embedded
Systems.)

\item Amir Hossein Ghamarian, Marc Geilen, Twan
Basten, Sander Stuijk. ``Parametric Throughput Analysis of
Synchronous Data Flow Graphs." \emph{Design, Automation and Test in
Europe, DATE 08}, Munich, Germany. March 10-14, 2008.

\item Amir Hossein Ghamarian, Marc Geilen, Sander Stuijk, Twan
Basten, Bart Theelen. ``Latency Minimization of Synchronous Data
Flow Graphs." \emph{10th Euromicro Conference on
Digital System Design, DSD 07}, Lubeck, Germany. August 27-31, 2007.

\item Amir Hossein Ghamarian, Marc Geilen, Sander Stuijk, Twan
Basten, Bart Theelen. ``Liveness and Boundedness of Synchronous Data
Flow Graphs." \emph{Formal Methods in Computer Aided Design, FMCAD
06}, San Jose, California, USA, November 12-16, 2006.

\item Sander Stuijk, Twan Basten, Marc Geilen, Amir Hossein Ghamarian and Bart D.
Theelen. ``Resource-Efficient Routing and Scheduling of
Time-Constrained Network-on-Chip Communication." \emph{9th Euromicro
Conference on Digital System Design, DSD 06}, Dubrovnik, Croatia,
30th August- 1st September, 2006.

\item Amir Hossein Ghamarian, Marc Geilen, Sander Stuijk, Twan Basten, Arno Moonen, Marco Bekooij, Bart Theelen, MohammadReza Mousavi.
``Throughput Analysis of Synchronous Data Flow Graphs." \emph{Sixth
International Conference on Application of Concurrency to System
Design, ACSD 06}, Turku, Finland, June 11-13, 2006.

\item Amir Hossein Ghamarian, ``An Evolutionary Algorithm for Graph
Coloring", \emph{M.S. Thesis}, Mathematical Sciences Department,
Sharif University of Technology, Tehran, Iran, January 2003 (in
Persian).

\item Amir Hossein Ghamarian, ``A Linux-based SMTP/POP3 Proxy", \emph{B.S.
Thesis}, Computer Engineering Department, Sharif University of
Technology, Tehran, Iran, September 2001 (in Persian).
\end{itemize}